Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-15 paper.qmd
Upated Figure 7

plot_predict_umap <- ggplot(data = predict_umap_scurve_scaled,
                            aes(
                              x = UMAP1,
                              y = UMAP2
                            )) +
  geom_point(alpha = 0.5)
```

@@

plot_predict_umap_model <- ggplot(data = jittered_points_df,
                            aes(
                              x = UMAP1,
                              y = UMAP2
                            )) +
  geom_point(alpha = 0.5)
```

@@

proj_plot_scurve_true <- ggplot(
  data = projected_df, 
  aes(
    x = proj1, 
    y = proj2)) +
    geom_point(alpha = 0.5)   
```

@@

plot_predict_umap_model_connect <- ggplot(data = predict_point_df,
                            aes(
                              x = UMAP1,
                              y = UMAP2, 
                              group = ID
                            )) +
  geom_point(alpha = 0.5) +
  geom_line(alpha = 0.3)
```

>>>>

plot_predict_umap <- ggplot(data = predict_umap_scurve_scaled,
                            aes(
                              x = UMAP1,
                              y = UMAP2
                            )) +
  geom_point(alpha = 0.5) +
  interior_annotation("b", c(0.92, 0.96))
```

@@

plot_predict_umap_model <- ggplot(data = jittered_points_df,
                            aes(
                              x = UMAP1,
                              y = UMAP2
                            )) +
  geom_point(alpha = 0.5) +
  interior_annotation("c", c(0.92, 0.96))
```

@@

proj_plot_scurve_true <- ggplot(
  data = projected_df, 
  aes(
    x = proj1, 
    y = proj2)) +
    geom_point(alpha = 0.5) +
  interior_annotation("a", c(0.92, 0.96))  
```

@@

plot_predict_umap_model_connect <- ggplot(data = predict_point_df,
                            aes(
                              x = UMAP1,
                              y = UMAP2, 
                              group = ID
                            )) +
  geom_point(alpha = 0.5) +
  geom_line(alpha = 0.3) +
  interior_annotation("d", c(0.92, 0.96))
```
